---
title: "IPM Analysis"
---

```{r libraries}
library(terra)
library(sf)
library(tidyverse)
library(tidyterra)
library(plotly)
```

```{r data}
year = 2023 # Change this value to the year you are interested in
orchards = st_read("data/orchards/orchards_utm11.shp") |>
            vect() |>
            mutate(conv = as.numeric({{year}} %in% c('CONV','UNKN')))
info = read.csv('data/pear_siteinfo.csv') |>
          select(c(str_glue('X{year}'), x, y, Code)) |>
          rename(conventional = str_glue('X{year}'))
# Change these files to get the data for the year you are interested in
taps = read.csv('data/pear_taps_2023.csv') # data pre-filtered to before August
brushes = read.csv('data/pear_leafbrush_2023.csv') # before July
```

```{r data_setup}
nymphs = brushes |>
          group_by(Plot) |>
          summarise(nymphs=sum(Nymphs))
preds = taps |>
          group_by(Plot) |>
          summarise(
                    trechnites=sum(Trechnites),
                    derae=sum(Derae_total),
                    campy=sum(Campy_total)
          )
ipm = info |>
          inner_join(nymphs, join_by(Code == Plot)) |>
          inner_join(preds, join_by(Code == Plot)) |>
          mutate(preds = trechnites + derae + campy,
                 conventional = as.logical(conventional))
```
```{r new_pipeline, warning = FALSE, message = FALSE}
source('zonal_analysis.R')

buff_width = 20 # This specifies the radial width of the buffer rings
# The first number is the lower bound for the buffers in meters
# The second number is the upper bound for the buffers in meters
buffs <- seq(200,1000,buff_width)
data.zone <- zonal_analysis(ipm, orchards, buffs, buff_width, map = TRUE)
```
  
Dark blue (non-exhaustively) represents conventionally managed orchards. 
Black dots represent study sites, and black areas represent a 1km buffer from those sites.

```{r t.test}
data.zone[[1]] |> t.test(nymphs ~ conventional, data = _)
```
The t-test does not find enough evidence to support the hypothesis that the conventional and non-conventional
study sites have an equal amount of scylla nymphs. Therefore, it appears as though organic and IPM orchards
do indeed have a lower nymph population overall. It seems beneficial to _not_ apply pesticides.

```{r nymph_modeling}
data.nonconv <- data.zone |> map(~filter(.,!conventional))
data.conv <- data.zone |> map(~filter(.,conventional))
linear.models.nonconv <- data.nonconv |>
                         map(~lm(nymphs ~ conv, data=.))
pvalues.nonconv <- linear.models.nonconv |>
                   map(~summary(.)$coefficients[2,4])
pvalues.nonconv |> map(~round(.,digits = 3)) |> flatten_dbl()
pvalues.nonconv |> flatten_dbl() |>  {\(x) x < 0.05}()
pvalues.nonconv |> flatten_dbl() |>  {\(x) x < 0.10}()
```
There aren't any significant linear relationships between % of conventionally managed land around the nonconventional study sites
when considering non-overlapping 20m wide ring buffers between 200m and 1000m at a signifiance level of 0.05 or 0.10.
```{r plots_nymph}
plots_nymph <- list(data.nonconv,data.conv) |>
  map2(
    c('Nonconventional', 'Conventional'),
    ~{
        .x |>
        map(as.data.frame) |>
        setNames(buffs) |>
        bind_rows(.id = 'id') |>
        mutate(id = as.numeric(id)) |>
        ggplot() +
        geom_point(mapping = aes(x=conv,y=nymphs,color=id)) +
        labs(color = 'buffer size (m) \n') +
        ggtitle(.y) +
        theme_bw()
  })

plots_nymph[[1]]
plots_nymph[[2]]
```

```{r a few individual plots}
data.nonconv |>
  tail(n=1) |>
  as.data.frame() |>
  ggplot() +
  ggtitle('1000m ring buffer (20m wide)') +
  geom_point(aes(x=conv,y=nymphs))
data.nonconv[[16]] |>
  as.data.frame() |>
  ggplot() +
  ggtitle('500m ring buffer (20m wide)') +
  geom_point(aes(x=conv,y=nymphs))
data.nonconv[[1]] |>
  as.data.frame() |>
  ggplot() +
  ggtitle('200m ring buffer (20m wide)') +
  geom_point(aes(x=conv,y=nymphs))
```
